Evaluating staged investments in critical infrastructure for climate adaptation

### 2019-04-11 slides-IPSWD/presentation.tex
Use biblatex

% Package List
\usepackage{
  amsmath,amssymb,                    % for more math commands
  array,                              % for custom table widths
  appendixnumberbeamer,               % don't count appendix slides in progress bar
  booktabs,                           % for better (alternative?) tables
  natbib,                             % references!
	physics,                            % for better notation
  siunitx,                            % for SI notation
}

@@

@@

\begin{frame}{The really big picture}
  \begin{figure}
    \centering
    \pause
    \includegraphics[height=0.325\textheight]{powerless.png}~
    \includegraphics[height=0.325\textheight]{ho-2017-1.png}\\
    \pause
    \includegraphics[height=0.325\textheight]{jongman-fig-2.jpg}~
    \includegraphics[height=0.325\textheight]{wapo-usa-temp.png}
  \end{figure}
  \nocite{economist-nigeria:2016,Ho:2017gy,Jongman:2012cr}
\end{frame}

@@

\begin{frame}[allowframebreaks]{References}
  \renewcommand*{\bibfont}{\scriptsize}
  \renewcommand{\bibsection}{}
  \nocite{DossGollin:TjTkb07T}
	\bibliographystyle{agu}
  \bibliography{library}
\end{frame}

@@

\begin{frame}{Hidden Markov Model}
  Two-state \gls{hmm} \citep[see][]{Rabiner:1986jk} implemented using pomegranate python package \citep{Schreiber:2017tg}.
  See package documentation for reference.
\end{frame}

>>>>

% Package List
\usepackage{
  amsmath,amssymb,                    % for more math commands
  array,                              % for custom table widths
  appendixnumberbeamer,               % don't count appendix slides in progress bar
  booktabs,                           % for better (alternative?) tables
	physics,                            % for better notation
  siunitx,                            % for SI notation
}

@@

\usepackage[
  backend=biber,
  doi=true,
  url=false,
  isbn=false,
  style=authoryear-comp, natbib=true,
  backref=false,
  maxbibnames=3,
  maxcitenames=2,
  uniquename=false,
  uniquelist=false
]{biblatex}
\renewbibmacro{in:}{}
\AtEveryBibitem{\clearfield{month}\clearfield{pages}}
\addbibresource{library.bib}

@@

\begin{frame}{The really big picture}
  \begin{figure}
    \centering
    \pause
    \includegraphics[height=0.325\textheight]{powerless.png}~
    \includegraphics[height=0.325\textheight]{ho-2017-1.png}\\
    \pause
    \includegraphics[height=0.325\textheight]{jongman-fig-2.jpg}~
    \includegraphics[height=0.325\textheight]{wapo-usa-temp.png}
  \end{figure}
  \citep{economist-nigeria:2016,Ho:2017gy,Jongman:2012cr}
\end{frame}

@@

\renewcommand*{\bibfont}{\small}
\begin{frame}[allowframebreaks]{References}
  \printbibliography[heading=none]
\end{frame}

@@

\begin{frame}{Hidden Markov Model}
  Two-state \gls{hmm} \citep[see][]{Rabiner:1986jk} implemented using pomegranate python package \citep{schreiber:2017}.
  See package documentation for reference.
\end{frame}
